Towards Verifying the Bitcoin-S Library

### 2019-06-21 paper/paper.tex
add specification

We can use equals (==) directly on Satoshis, because it is a case class.
The addition will now look like this:
\begin{lstlisting}[style=scala]
  override def +(c: CurrencyUnit): CurrencyUnit = {
    require(c.satoshis == Satoshis.zero)
    Satoshis(satoshis.underlying + c.satoshis.underlying)
  } ensuring(res => res.satoshis == this.satoshis)
\end{lstlisting}

>>>>

We can use equals (==) directly on Satoshis, because it is a case class.

Before:
\begin{lstlisting}[style=scala]
sealed abstract class CurrencyUnit {
  def satoshis: Satoshis

  protected def underlying: Int64
}
\end{lstlisting}

The addition will now look like this:
\begin{lstlisting}[style=scala]
sealed abstract class CurrencyUnit {
  def satoshis: Satoshis

  override def +(c: CurrencyUnit): CurrencyUnit = {
    require(c.satoshis == Satoshis.zero)
    Satoshis(satoshis.underlying + c.satoshis.underlying)
  } ensuring(res => res.satoshis == this.satoshis)

  protected def underlying: Int64
}
\end{lstlisting}
